Type cones of $\b{g}$-vector fans

### 2019-03-07 thirdPaper/draft/typeConeAssociahedra.tex
added assumptions in Proposition 4.30

\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
 The proof is know similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
\end{proof}

@@

%%
\subsubsection{Objects presented by a rigid object}\label{sect::Rigid}

We know describe a setup satisfying the assumptions of Section~\ref{sect::setting} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}

@@

\begin{lemma}
 The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
\end{lemma}

@@

\begin{proposition}
Assume that
Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of Section~\ref{sect::setting}.
\end{proposition}

\begin{proof}
For any~$T\in\tc$ the existence of an extriangle~$0\infl T\defl T\overset{0}{\dashrightarrow}$ shows that~$\tc$ is a full subcategory of~$\cat$.

>>>>

\begin{proof}[Proof of Theorem~\ref{theorem::extricats}]\yann{PG: Est-ce que cela te semble suffisant, ou veux-tu que j'ajoute des d\'etails ? }
 The proof is now similar to the proof of Theorem~\ref{theo::relations-g-vecteurs}, by using Proposition~\ref{prop::KRextricat} instead of Proposition~\ref{prop::functor-F}, Proposition~\ref{prop::index iso extricat} instead of Corollary~\ref{coro::grothendieck-g-vectors}, and the fact that~$\tc$ is made of projective objects instead of Lemma~\ref{lemm::almost-split}.
\end{proof}

@@

%%
\subsubsection{Objects presented by a subcategory}\label{sect::prT}

We know describe a setup satisfying the assumptions of Section~\ref{setting::extricat} that, at the same time, subsumes all examples given so far, while being easily checked in practice.\yann{A reformuler...}

@@

\begin{lemma}\label{lemma:: prT is extriangulated}
 The full subcategory~$\cat$ is extension-closed in~$(\ec,\mathbb{E}_\tc,\mathfrak{s}_\tc)$, and thus inherits an extriangulated structure.
\end{lemma}

@@

\begin{notation}
 Write~$\tc^\perp$ for the full subcategory of~$\ec$ whose objects are those objects~$X\in\ec$ that satisfy~$\ec(T,X)=0$, for any~$T\in\tc$.
\end{notation}

\begin{proposition}\label{prop::prT}
Assume that, for any~$T\in\tc$, there is an~$\mathfrak{s}$-conflation~$T\infl 0\defl X_T$ in~$\ec$ with~$X_T\in\tc^\perp$.
Then the extriangulated category~$\cat$ satisfies the assumptions (1) to (3) of Section~\ref{setting::extricat}.
\end{proposition}

\begin{proof}
For any~$T\in\tc$ the existence of an extriangle~$0\infl T\defl T\overset{0}{\dashrightarrow}$ shows that~$\tc$ is a full subcategory of~$\cat$.
By Lemma~\ref{lemma:: prT is extriangulated}, the category~$\cat$ is extriangulated and, by definition of this extriangulated structure, the objects in~$\tc$ are projective in~$\cat$.
Assumption (3) is satisfied by the definition of~$\cat$, and assumption (2) is equivalent to that of the proposition.
\end{proof}

\begin{remark}
 The categories considered in Sections~\ref{sect::2CYTriangulated},~\ref{sect::2CYexact} and~\ref{sect::Kbproj} all fall into the setting of Proposition~\ref{prop::prT}.
\end{remark}
